### 2015-02-22 fundamentals/intro.tex
cleaned up last sentence of IA

\Cyclus emerged from a line of tools seeking to break this practice.  Its
precursor,
\gls{GENIUS} Version 1 \cite{dunzik-gougar_global_2007,jain_transitioning_2006},
originated within \gls{INL} and sought to provide generic regional capability.
Based on lessons learned from \gls{GENIUS} Version 1, the \gls{GENIUS} Version
2 \cite{oliver_studying_2009,huff_geniusv2_2009} simulator sought to provide more
generality and an extensible interface to facilitate collaboration.  The
\Cyclus project then improved upon the \gls{GENIUS} effort by
implementing increased modularity and encapsulation.  The result is a dynamic
simulator that treats both materials and facilities discretely, with an
architecture that permits multiple and variable levels of fidelity. The
simulator's agent-based framework for tracking the transformation and trade of
resources between autonomous regional and institutional entities with
customizable behavior and objectives is an innovation not pursued by any
existing fuel cycle simulator.

>>>>

\Cyclus emerged from a line of tools seeking to break this practice.  Its
precursor, \gls{GENIUS} Version 1
\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, originated within
\gls{INL} and sought to provide generic regional capability.  Based on lessons
learned from \gls{GENIUS} Version 1, the \gls{GENIUS} Version 2
\cite{oliver_studying_2009,huff_geniusv2_2009} simulator sought to provide more
generality and an extensible interface to facilitate collaboration.  The \Cyclus
project then improved upon the \gls{GENIUS} effort by implementing increased
modularity and encapsulation.  The result is a dynamic simulator that treats
both materials and facilities discretely, with an architecture that permits
multiple and variable levels of fidelity. Using an agent-based framework, the
simulator tracks the transformation and trade of resources between autonomous
regional and institutional entities with customizable behavior and
objectives. This capability is an innovation not pursued by any existing fuel
cycle simulator.
